RDT - Gold Standard Equivalence

### 2022-01-18 RDT-equivalence.rmd
Create shiny app and explore effects of sens and spec on test results
Only just started the shiny app, but have contour plots for number of test positive, and PPV, and table describing the values by two different types of tests (Gold Standard and Rapid)

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(hrbrthemes)
library(kableExtra)
library(lubridate)
library(glue)
library(paletteer)
```

@@

```{r}

```

>>>>

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(hrbrthemes)
library(kableExtra)
library(lubridate)
library(purrr)
library(glue)
library(MetBrewer)
```

@@

```{r}
sens_range <- seq(0, 1, 0.05)
spec_range <- seq(0, 1, 0.05)
data <- tidyr::crossing(sens_range, spec_range)
```

```{r}
prev <- 0.05
tot <- 100

dis_pos <- tot * prev
dis_neg <- tot * (1 - prev)
```

```{r}
test <- map2_dfr(
  .x = data$sens_range,
  .y = data$spec_range,
  .f = function(.x, .y){
    true_pos <- dis_pos * .x
    true_neg <- dis_neg * .y
    false_pos <- dis_neg * (1 - .y)
    false_neg <- dis_pos * (1 - .x)

    test_pos <- true_pos + false_pos
    test_neg <- true_neg + false_neg

    ppv <- true_pos / test_pos
    npv <- true_neg / test_neg

    tibble(
      sens = .x,
      spec = .y,
      true_pos = true_pos,
      true_neg = true_neg,
      false_pos = false_pos,
      false_neg = false_neg,
      test_pos = test_pos,
      test_neg = test_neg,
      ppv = ppv,
      npv = npv
    )
  }
)
```

```{r}
ggplot(test, aes(x = sens, y = spec, z = test_pos)) +
  geom_contour_filled() +
  scale_fill_manual(values = met.brewer("OKeeffe2", 10)) +
  labs(
    title = "Number of Positive Tests by Sensitivity and Specificity",
    subtitle = glue("Prevalence = {prev}, Total Tests = {tot}, Disease Positives = {dis_pos}"),
    x = "Sensitivity",
    y = "Specificity",
    fill = "Number of Positive Tests"
  ) +
  theme(legend.position = "bottom")
```

```{r}
ggplot(test, aes(x = sens, y = spec, z = ppv)) +
  geom_contour_filled() +
  scale_fill_manual(values = met.brewer("Hokusai2", 10)) +
  labs(
    title = "PPV by Sensitivity and Specificity",
    subtitle = glue("Prevalence = {prev}, Total Tests = {tot}, Disease Positives = {dis_pos}"),
    x = "Sensitivity",
    y = "Specificity",
    fill = "PPV"
  ) +
  theme(legend.position = "bottom")
```
